---
title: "HW6"
author: "Liner Ge"
date: "2020/12/4"
output: github_document
---
```{r}
library(tidyverse)
library(readxl)
library(patchwork)
library(modelr)
library(mgcv)
set.seed(1)
```

# Problem 1

read in data
```{r}
homicide_df =
  read_csv("./data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Try this across cities

```{r}
models_results_df =
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
    ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate), # odds ratio
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))

```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Problem 2

## read in and tidy the data 

```{r}
birtnweight_df = 
  read.csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>%
  filter(frace != 9) %>% 
  drop_na() %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
    ),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"
    ),
    mrace = case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other"
    ),
    malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"
    ),
    across(where(is.character), as.factor)
    )
```

## Model selection

```{r}
birtnweight_df %>% 
  lm(bwt~.,data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

I assume that baby's weight is associated with physiological conditions of his/her mother' pregnancy. According to the regression model of all veriable, I would choose variables with p.value smaller than 0.05. Thus, I choose  mother’s age at delivery `momage`, mother’s weight gain during pregnancy `wtgain`, gestational age in weeks`gaweeks`, number of live births prior to this pregnancy`parity` as predictors.

```{r}
fit_1 = lm(bwt ~ momage +  wtgain + gaweeks + parity, data = birtnweight_df)

fit_1 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

fit_1_df = 
  birtnweight_df %>% 
  select(bwt, momage, wtgain, gaweeks, parity) %>% 
  modelr::add_residuals(fit_1) %>% 
  modelr::add_predictions(fit_1)
```

## Plot of model residuals against fitted values

```{r}
fit_1_df %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", color = "red", linetype = 2) + 
  labs(
    title = "Plot of model residuals against fitted values",
    x = "Predictions",
    y = "Residuals"
  )
  
```

## The other two models

```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = birtnweight_df)

model_1 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

```{r}
model_2 = lm(bwt ~ bhead * blength * babysex, data = birtnweight_df)

model_2 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

```{r}
cv_df = 
  crossv_mc(birtnweight_df, 200) %>% 
   mutate(
        train = map(train, as.tibble),
        test = map(test, as.tibble)
    )

cv_birthweight = 
  cv_df %>% 
    mutate(
        my_model = map(train, ~lm(bwt ~ momage +  wtgain + gaweeks + parity, data = .x)),
        model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
        model_2 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
    ) %>% 
    mutate(
        rmse_my_model = 
          map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
        rmse_model_1 = 
          map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
        rmse_medel_2 = 
          map2_dbl(model_2, test, ~rmse(model = .x, data = .y))
    )

cv_birthweight %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
        title = "Cross Validation Comparisons",
        x = "Models",
        y = "RMSE")
```

According to the comparisons, I find my model has the highest rmse, which means this is the worst model among these three. Model 2 has the lowest rmse and can be the reasonable choice.

# Problem 3
read in data

```{r}
weather_df = 
  read.csv("./data/df.csv")
```

```{r}
bootstrap_results = 
  weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result_tidy = map(models, broom::tidy),
    result_glance = map(models, broom::glance)) %>% 
  unnest(result_tidy, result_glance) %>% 
  select(id = .id, term, estimate, r_squared = r.squared)

bootstrap_results %>% head() %>% knitr::kable()
```

## Distribution of r^2

```{r}
bootstrap_results %>%
  ggplot(aes(x = r_squared)) +
  geom_density() +
  labs(
        title = "Distribution of r^2"
    )
```

The distribution of r^2 is approximately normal. According to this plot, it is distributed around 0.88 and 0.94, really close to 1, which means the model fit well and y can be well explained by x.

```{r}
bootstrap_results %>%
  select(id, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>% 
  rename(intercept = `(Intercept)`) %>% 
  mutate(
    log_beta01 = log(intercept*tmin)
  ) %>% 
  ggplot(aes(x = log_beta01)) +
  geom_density() +
  labs(
        title = "Distribution of log(β0 x β1)",
        x = "log(β0 x β1)"
    )
```

The distribution of log(β0 x β1) is approximately normal, too. The mean of it is about 4.33.
```{r}
quantile(bootstrap_results$r_squared, probs = c(0.025,0.975)) %>% knitr::kable(caption = "95% CI for r^2")
```

```{r}
quantile(bootstrap_results$log_beta, probs = c(0.025,0.975)) %>% knitr::kable(caption = "95% CI for log(β0 x β1)")
```

